---
title: "S631 HW1"
author: "Wencao Yang"
date: "September 4, 2016"
output: html_document
---


## ALR 1.1
```{r}
library(alr3)
rm(list=ls())
meanLength <- with(wblake, tapply(Length, Age, mean))
varLength <- with(wblake, tapply(Length, Age, var))
meanLength
varLength
plot(1:8, meanLength)
```

exactly the dashed line in fig 1.5 in ALR book
```{r}
plot(1:8, sqrt(varLength))
```

no pattern can be found in the standard deviation plot

## ALR 1.2

##1.2.1
Here is the summary of temperature vs month
```{r}
head(Mitchell)
summary(Mitchell)
##and here is the intercept and slope
m0<-lm(Temp~Month,data=Mitchell)
print(coef(m0))

plot(Temp~Month,data=Mitchell)
abline(m0)
```

It's clear that the temperature has an average around 10 C and it increases slowly with month

##1.2.2
I don't know how to strech the x axis now so I think the an easy way to do this is to only draw 1/4 of the x axis, it's clear we can see a sin curve on this graph,indicatig the flutuation of temperature with month, and the statistics results are the same with 1.2.1 
```{r}
plot(Temp~Month,data=Mitchell,xlim=c(0,50))
```


## ALR 1.4
```{r}
head(oldfaith)
plot(Interval~Duration,data=oldfaith)
m1<-lm(Interval~Duration,data=oldfaith)
print(coef(m1))
abline(m1)
```

$Interval=0.17686*Duration+33.98781$
