---
title: "S631 HW2"
author: "Wencao Yang"
date: "September 8, 2016"
output: pdf_document
---
# ALR 2.2
```{r}
library(alr4)
head(UBSprices)
plot(rice2009~rice2003,data=UBSprices,ylim=c(0,100))
abline(0,1)
```

## ALR 2.2.1
The points above y=x line indicate the rice price increase from 2003 to 2009 while the points below points indicate the rice price decrease from 2003 to 2009

## ALR 2.2.2
Vilnius has the largest price increase and Mumbaio has the largest price decrease based on the figure in textbook

## ALR 2.2.3
No, it doesn't suggest the price in 2009 lower than in 2003. First it varies in different cities, second, it's only the rice price

## ALR 2.2.4
```{r}
m0<-lm(rice2009~rice2003,data = UBSprices);
beta0=coefficients(m0)[1];
beta1=coefficients(m0)[2];
fittedNumber=beta0+beta1*UBSprices$rice2003
residual=UBSprices$rice2009-beta0-beta1*UBSprices$rice2003;
plot(residual~fittedNumber,data=UBSprices)
abline(0,0)
```
First,The residual versus fittednumber indicates the failure of simple linear regression since it's not a null plot.
Second,we have some cities far away from the rest, which may make the result not very resonable
And there should be many factors influncing the rice2009, a single variable rice2003 is not enough to predict the rice2009 in real life

# ALR 2.8

## ALR 2.8.1
$\alpha$ is the expect value using the fitting model $\beta_0$+$\beta_1x$ where $x$ is the average $\bar{x}$

## ALR 2.8.2
$(i)$ $\hat{\alpha}=\bar{y}$:

Now we have $RSS=\sum(y_i-\hat{\alpha}-\hat{\beta}_1(x_i-\bar{x}))^2$
let $\frac{\partial RSS}{\partial \hat{\alpha}}=0$ we have $\sum(y_i- \hat{\alpha}-\hat{\beta_1}(x_i-\bar{x}))=0$, i.e.,$n\bar{y}-n \hat{\alpha}-\sum(x_i-\bar{x})=0$, i.e.,$\hat{\alpha}=\bar{y}$

$(ii)$ $\hat{\beta_1}=\frac{SXY}{SXX}$:

let $\frac{\partial RSS}{\partial \hat{\beta_1}}=0$,
We have $\sum (y_i-\hat{\alpha}-\hat{\beta_1}(x_i-\bar{x}))(x_i-\bar{x})$
which leads to $x_iy_i-\sum y_i\bar{x}-\sum\bar{y}x_i+\sum\bar{x}\bar{y}-hat{\beta_1}(x_i-\bar{x})^2=0$,i.e.,$\sum x_iy_i-n\bar{x}\bar{y}=\hat{\beta_1}(x_i-\bar{x})^2$,i.e.,$\hat{\beta_1}=\frac{\sum x_iy_i-n\bar{x}\bar{y}}{\sum x_i^2-n\bar{x}^2}$,i.e., $\hat{\beta_1}=\frac{SXY}{SXX}$

$(iii)$ $E(\hat{\alpha}|X)$:
$\hat{\alpha}$ is a linear combination of $y_i$, $\hat{\alpha}=\sum \frac{1}{n}y_i=\bar{y}$
so $E(\hat{\alpha}|X)=E(\bar{y}|X)=\alpha$

$(iv)$ $E(\hat{\beta_1}|X)$:
$\hat{\beta_1}$ is also a linear combination of $y_i$, $\hat{\beta_1}=\sum C_iy_i$, where $C_i=\frac{x_i-\bar{x}}{SXX}$, 
$E(\hat{\beta_1}|X)=E(\sum C_iy_i|X)=\beta_1$