---
title: "S631 HW3"
author: "Wencao Yang"
date: "September 14, 2016"
output: html_document
---
# ALR 2.6

## ALR 2.6.1 & 2.6.2
```{r}
library(alr4)
head(ftcollinstemp)
plot(winter~fall,data=ftcollinstemp)
m0=lm(winter~fall,data=ftcollinstemp)
abline(m0)
summary(m0)
```
The 2-side test gives a t value of 2.049 and P vaule of 0.0428, which means we should reject the null hypothesis,i.e., the slope=0.The summary is lised below.

## ALR 2.6.3
```{r}
SYY=sum((ftcollinstemp$winter-mean(ftcollinstemp$winter))^2)
r2=summary(m0)$r.squared
SSreg=r2*SYY
```
The winter varility explained by fall is 42.44576 which is coefficient of determination times SYY

## ALR 2.6.4
Just divide the data into 2 groups called "early" and "later" and do the same thing. It's clear that the slope becomes smaller after the year of 1989 compared with before.
```{r}
early<-subset(ftcollinstemp,year>1900|year<1989)
later<-subset(ftcollinstemp,year>1989)
m1=lm(winter~fall,data=early)
m2=lm(winter~fall,data=later)
plot(winter~fall,data=early)
abline(m1)
summary(m1)
plot(winter~fall,data=later)
abline(m2)
summary(m2)
```

# ALR 2.16

## ALR 2.16.1-2.16.4
```{r}
head(UN11)
plot(log(fertility)~log(ppgdp),data=UN11)
m3=lm(log(fertility)~log(ppgdp),data=UN11)
abline(m3)
summary(m3)
summary(m3)$r.squared
```
The summary gives the 2-side test result and the P value of 1-side result is just half of that in the 2-side test and it's close to zero.the significant level is more than 0.9999... that's to say we are pretty sure the fertility decreases with the ppgdp
the coefficient of determination means how much sum of square due to the regression, here it's 0.5259.

## ALR 2.16.5
```{r}
new <- data.frame(ppgdp = 1000)
predict(m3,new,interval="confidence",level=0.95)
```
the 95% CI is (1.173808,1.295327)
So the 95% CI for fertility is (exp(1.173808),exp(1.295327))=(3.2342,3.65219)
```{r}
exp(1.173808)
exp(1.295327)
```

## ALR 2.16.6
```{r}
subset(UN11,UN11$fertility==max(UN11$fertility))
subset(UN11,UN11$fertility==min(UN11$fertility))
r=residuals(m3)
sort(r)
```
sort(r) gives the localities of largest 2 positive residual:
Angola , Equatorial Guinea 
the localities of largest 2 negative residual:
Bosnia and Herzegovina, Moldova