---
title: "S631 HW6"
author: "Wencao Yang"
date: "10/14/2016"
output: html_document
---

#1 ALR4 problem 3.6

##3.6.1 and 3.6.2
```{r}
library(alr4)
head(water)
scatterplotMatrix(~BSAAM+OPBPC+OPRC+OPSLAKE,data = water)
m0=lm(BSAAM~OPBPC+OPRC+OPSLAKE,data = water)
summary(m0)
cor(water)
```
The correlation matrix shows that correlation between BSAAM,OPBPCC,OPRC,OPSLAKE are big and positive, which is indicated by the scatterplot Matrix

t value of OPBPC is close to zero, which means OPBPC slope is very possible to be zero, t value of OPRC and OPSLAKE is big and lead to a small P value which means slope of OPRC and OPSLAKE is not zero

#2 

## a)
```{r}
x0<-rep(1,length(water$OPBPC))
x1<-c(water$OPBPC)
x2<-c(water$OPRC)
x3<-c(water$OPSLAKE)
X=cbind(x0,x1, x2, x3)
inv=solve(t(X)%*%X)
H=X%*%inv%*%t(X)

```

## b)
```{r}
qr(inv)$rank
qr(H)$rank
```
It's clear that rank of inv is 4.
H is symmetric and idempotent so rank(H) is tr(H)=p+1, p=3, so rank(H)=4 

## c)
```{r}
Y<-c(water$BSAAM)
betaMatrix=inv%*%t(X)%*%Y
RSS=8304^2*39
n=length(water$OPRC)
p=3
variance=RSS/(n-p-1)
se_beta_1=sqrt(variance*inv[1,1])
se_beta_2=sqrt(variance*inv[2,2])
se_beta_3=sqrt(variance*inv[3,3])
se_beta_4=sqrt(variance*inv[4,4])
se_beta_1
se_beta_2
se_beta_3
se_beta_4
```
 
## d)
```{r}
SSY=sum((Y-mean(Y))^2)
SSreg=SSY-RSS
RSS
SSY
SSreg
anova(m0)
```
The RSS is the same with the result in anova(m0)

#3 ALR4 problem 4.2
```{r}
head(Transact)
a=(Transact$t1+Transact$t2)/2
d=(Transact$t1-Transact$t2)
m1=lm(time~t1+t2,data=Transact)
m2=lm(time~a+d,data=Transact)
m3=lm(time~t2+d,data=Transact)
m4=lm(time~t1+t2+a+d,data=Transact)
summary(m1)
summary(m2)
summary(m3)
summary(m4)
```

## 4.2.1
coeff of a and d are NA in M4. That's because a and d are linear combination of t1 and t2

## 4.2.2
The intercept and standard error are the same for all models
t1 in M1 and M4 are the same with d in M3
d in M2 and d in M3 are different

## 4.2.3
M1
             Estimate Std. Error t value Pr(>|t|)    
t2            2.03455    0.09434  21.567   <2e-16 ***

M3
            Estimate Std. Error t value Pr(>|t|)    
t2            7.4966     0.3654  20.514   <2e-16 ***

They are different because the other regressor is t1 and t1-t2,respectively. The correlation between t1 and t2 is different with the correlation between t1-t2 and t2