---
title: "S631 HW8"
author: "Wencao Yang"
date: "11/4/2016"
output: html_document
---

#1 ALR4 problem 5.16

## 5.16.1
```{r}
rm(list = ls())
library(alr4)
head(cathedral)
Romanesque=subset(cathedral,Type=='Romanesque')
Gothic=subset(cathedral,Type=='Gothic')
m0=lm(Height~Length,data=Romanesque)
m1=lm(Height~Length,data=Gothic)
plot(Romanesque$Height~Romanesque$Length)
abline(m0)
plot(Height~Length,data=Gothic)
abline(m1)
```

The Romanesque style: Height more concentrated around 75, no heavy dependence on length, 

The Gothic style: Height incresae with length, the range is bigger than Romanesque style, relationship is obvious

## 5.16.2
```{r}
summary(m0)
summary(m1)
```
t test gives the P value for 2 styles, which support the visual result from graph. For m0, P value is big which means we cannot reject null hypothesis,i.e., height may be independent of length.For m1, P value is small which means we should reject null hypothesis,i.e., height dependends on length.

#2 ALR4 problem 5.20

## 5.20.1
```{r}
head(domedata)
scatterplotMatrix(~Cond+Velocity+Angle+BallWt+BallDia+Dist,data=domedata)
m2=lm(Dist~Cond+Velocity+Angle+BallWt+BallDia,data=domedata)
summary(m2)
```
The fan does affect the ball distance.The distance can be canged by condition, velocity and balldiameter.

## 5.20.2
```{r}
head(domedata1)
scatterplotMatrix(~Date+Cond+Velocity+Angle+BallWt+BallDia+Dist,data=domedata1)
m3=lm(Dist~Date+Cond+Velocity+Angle+BallWt+BallDia,data=domedata1)
summary(m3)
```
The 2 experiments results are different. The date does affect the result which means the way to manipulate fans can affect the result.Distance has a bigger range on May.

#3 ALR4 problem 6.6
```{r}
head(fuel2001)
m3=lm(FuelC~Drivers+Income+Miles+MPC+Pop+Tax,data = fuel2001)
summary(m3)
```
For the overall F test
NH:FuelC=intercept
AH:FuelC=intercept+Drivers+Income+Miles+MPC+Pop+Tax

F test gives P value of 2.2e-16 which means we should reject NH. That means null model is not right in this case.